\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\setlength{\parindent}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\textbf{\Huge Zhenliang Ju} \\
\vspace{4pt}
\small \texttt{Tel:186-0123-9387} $|$
\href{mailto:juzhenliang@hotmail.com}{\underline{juzhenliang@hotmail.com}} $|$
\href{https://linkedin.com/in/wargrey}{\underline{LinkedIn:wargrey}} $|$
\href{https://github.com/wargrey}{\underline{Github:wargrey}}

%-----------SUMMARY-----------
\section{Summary}
I design and build software systems from scratch to structure and visualize complex domain knowledge.
My work spans industrial control and educational software, centered on systems that evolve and transfer across domains,
enabled by domain-specific languages and semantic visualization for modeling, reasoning, and learning.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Self-employed}{Yiwu, Zhejiang, China}
      {Independent Developer \& Instructor}{Jul. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Partnered with Yiwu Qingwu Arts Center
          for CSP/J training and Futian Second Primary School for public Python-based
          IT curricula and clubs; focused on adapting formal algorithm design and high-level
          computational concepts for diverse institutional requirements.}
        \resumeItem{Formalized the architecture of a teaching system into a thesis-scale document.}
        \resumeItem{Synthesized prior experience in industrial control systems
          and educational software into a unified approach to system design and
          representation, bridging the gap between engineering practice and learning
          environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Zhenjiang Luokebai Training Center Co., Ltd.}{Zhenjiang, Jiangsu, China}
      {STEM Instructor \& Curriculum Developer}{Mar. 2021 -- Jun. 2024}
      \resumeItemListStart
        \resumeItem{Architected and maintained a high-performance C++ teaching engine derived
          from industrial control logic to simulate complex system behaviors for learning environments.}
        \resumeItem{Applied formal engineering principles—including state
          modeling and modular design—to restructure complex scientific curriculum into
          machine-executable and visually verifiable logic.}
        \resumeItem{Utilized high-frequency user interaction data to
          iteratively refine engine architecture, ensuring long-term coherence between
          language semantics and visual feedback.}
        \resumeItem{Partnered with Zhenjiang Peiwen
          Experimental School to deploy a comprehensive science curriculum for
          compulsory education; managed the full lifecycle from hands-on experiments
          and project-based learning (PBL) to standardized assessments and
          competitive mentoring.}
      \resumeItemListEnd

    \resumeSubheading
      {Zhenjiang Mingrun Information Technology Co., Ltd.}{Zhenjiang, Jiangsu, China}
      {Software Engineer}{Aug. 2017 -- May 2020}
      \resumeItemListStart
        \resumeItem{Designed and implemented a full
          dredging control system on the UWP platform from scratch, replacing legacy
          Win32 systems with a unified, high-reliability architecture deployed on real
          industrial vessels.}
        \resumeItem{Developed a custom GUI framework to translate
          raw numerical sensor data into structured visual representations (e.g., drag
          arms, hydraulic systems, GPS-integrated spatial tooling),
          significantly improving operational clarity for non-technical crew.}
        \resumeItem{Partnered with ship operators and domain
          experts to formalize fragmented, non-technical knowledge into coherent
          system behaviors.}
        \resumeItem{Conducted 3 months of continuous onboard
          testing to ensure stability under harsh maritime conditions, iterating the system
          based on real-world feedback loops.}
        \resumeItem{Established core design principles (clarity over ornamentation) that
          later served as the foundation for a teaching-oriented
          software engine.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Graphics} $|$ \emph{Typed Racket, C}}{\textbf{October 2014 -- Present}}
          \resumeItemListStart
            \resumeItem{Sustained \textbf{long-term evolution} of the system through rigorous abstraction design and engineering practices}
            \resumeItem{Designed and built a compositional, multi-collection DSL ecosystem for semantic visualization and diagram generation}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{digimon} $|$ \emph{Typed Racket, C}}{\textbf{Apirl 2017 -- Present}}
          \resumeItemListStart
            \resumeItem{Built custom C++ build systems and tooling to abstract away industry-standard complexity,
              optimizing the "mental model" for users learning systems programming}
            \resumeItem{Developed a specification-driven testing framework with beginner-friendly diagnostics,
              supporting evaluation workflows similar to competitive programming environments}
            \resumeItem{Implemented core components of the zlib compression algorithm to support data formats and protocols (e.g., PNG, OOXML) that rely on it}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{JrSTEM} $|$ \emph{Typed Racket, Scribble, C++, tex, HTML/CSS}}{Apirl 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Developed and maintained a code-driven content system for producing structured computer science learning materials}
            \resumeItem{Designed a Scribble-based documentation pipeline to generate and manage educational content as part of the codebase}
            \resumeItem{Applied a domain-specific representation framework to encode and deliver programming concepts through executable teaching materials}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Nanjing University of Aeronautics and Astronautics}{Nanjing, Jiangsu, China}
      {Bachelor of Engineering in Computer Science}{Part-time, 2025}
    \resumeSubheading
      {Changshu Institute of Technology}{Changshu, Jiangsu, China}
      {Associate's in Software Engineering}{2010}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{
  \textbf{Programming Languages}{: Typed Racket, C++, C, HTML/CSS, Java} \\
  \textbf{Databases}{: MySQL, SQLite, Oracle} \\
  \textbf{Tools \& Technologies}{: LaTeX, Scribble, Content Pipelines, Build Systems} \\
  \textbf{Areas}{: DSL Design, Visualization, System Design, Educational Systems}
}
}
\end{itemize}

\end{document}
